All Samples Model

### 2018-08-14 AllSamplesModel.Rmd
adding residuals

qq = quantile(ch$hazards, seq(0,1,.15))
p = ggplot(ch, aes(coef, hazards, col=hazards >= qq[length(qq)])) + 
  geom_point(alpha=0.8, show.legend = F) + 
  geom_text_repel(aes(x=coef, label=ifelse(hazards >= qq[length(qq)], label, '')),show.legend=F) +
  scale_color_manual(values=c('firebrick3','darkblue')) +
  labs(title='Top features by hazard ratio', x='Coefficient value', y='Hazard') + plot.theme 
p

>>>>

qq = quantile(ch$hazards, seq(0,1,.15))
p = ggplot(ch, aes(coef, hazards, col=hazards >= qq[length(qq)])) + 
  geom_point(alpha=0.8, show.legend = F) + 
  geom_text_repel(aes(x=coef, label=ifelse(hazards >= qq[length(qq)], label, '')),show.legend=F) +
  scale_color_manual(values=c('firebrick3','darkblue')) +
  labs(title='Features by CV(relative risk)', x='Coefficient value', y='CV(RR)') + plot.theme 
p
